---
title: "mendeleyr"
author: "Sergio Oller"
date: "`r Sys.Date()`"
output: rmarkdown::github_document
---

mendeleyr provides a subset of the Mendeley API through R.

[![Build Status](https://travis-ci.org/zeehio/mendeleyr.svg?branch=master)](https://travis-ci.org/zeehio/mendeleyr)


## Browse source code

Checkout the code and browse it at
[http://github.com/zeehio/mendeleyr](http://github.com/zeehio/mendeleyr).

## How to install mendeleyr:

### Package installation

* To install the latest development version: 

    ```
    devtools::install_github("zeehio/mendeleyr")
    ```

## Quick start:

### Setup:

Mendeley's API is based on oAuth2. This means that mendeleyr should be registered
as an application in [http://dev.mendeley.com/myapps.html] and receive a `client_id`
and a `client_secret`. As `mendeleyr` is open source, the package can't provide
a secret so it is required that the `mendeleyr` user registers its own app.

Fortunately it's an easy step, and `mdl_conf_new()` provides detailed instructions on
how to do that:

```{r, error=TRUE}
library(mendeleyr)
mdl_conf_new()
```

Once you have registered you app, you will be able to save the secret to a file.

```{r, eval=FALSE}
mdl_conf_save(client_id = "given-by-mendeley", client_secret = "given-by-mendeley",
              where = "/choose/a/path/mendeley_conf.json")
```

The final step is to grant `mendeleyr` access to your account. Your web browser
will open and ask you login and authorize. With this `mendeleyr` never sees your
username and password :-)

```{r, eval = FALSE}
token <- mdl_token("/choose/a/path/mendeley_conf.json")
```

### Using mendeleyr



#### Export mendeley folders to a bibtex file:

```{r, eval = FALSE}
all_my_folders <- mdl_folders(token)
mdl_to_bibtex(token, folder_name = "my_folder", bibfile = "my_folder.bib")
```

But we can work with groups as well:

```{r, eval = FALSE}
all_folders_from_a_group <- mdl_folders(token, group_name = "my_group")

mdl_to_bibtex(token, folder_name = "shared_folder", group_name = "my_group",
              bibfile = "shared_folder.bib")
```

#### Download a file:

```{r, eval = FALSE}
my_docs <- mdl_documents(token, folder_name = "my_folder")
all_files <- mdl_files(token, document_id = my_docs$id[1])
mdl_download_file(token, all_files[1,])
```


